Helmet Foam Case Study Report

### 2024-05-02 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd

@@

The summary of this model shows a high significance in almost all of our coefficients through small p-values. The only value that does not show a significant p-value is chemIndex, however we chose to keep that in the model because of how significant the interaction between chemIndex and log(cycle) is. This model has multiple interactions: porosity and log(cycle), frequency and log(cycle), and chemical index and log(cycle). These interactions show that if all other variables are held constant, there is a combined effect of these interactions on the response variable.

@@

**Question 1:** We see that porosity, chemical index, and cycle number have the most significant effects on damping and stiffness. Frequency also has a significant effect, but only on damping.

>>>>

FactorModel <- lmer(log(stiffnessFrac) ~  factor(chemIndex) + freq + amp +  log(cycle) +  factor(chemIndex):log(cycle) + freq:log(cycle) + amp:log(cycle) + (1 + log(cycle)|ID), data = foam_data_scaled)

@@

The summary of this model shows a high significance in almost all of our coefficients through small p-values (less than 0.05). These small p-values suggest that these variables are significant predictors of our response variable. The only value that does not show a significant p-value is chemIndex, however we chose to keep that in the model because of how significant the interaction between chemIndex and log(cycle) is. This model has multiple interactions: porosity and log(cycle), frequency and log(cycle), and chemical index and log(cycle). These interactions show that if all other variables are held constant, there is a combined effect of these interactions on the response variable.

@@

**Question 1:** We see that chemical index, frequency, and cycle number have the most significant effects on both damping and stiffness. However porosity has an effect on damping and amplitude as an effect on stiffness.
